February 2nd, 2016

\ifplastex
\subsubsection{Usage Of Content}
\label{sec:usage-content}
\else
  \ifstandalone
  \subsubsection{Usage Of Content}
  \label{sec:usage-content}
  \else
  \section{Usage Of Content}
  \label{sec:usage-content}
  \fi
\fi

All intellectual property rights existing in this information remain
the property of the Secretary of State for Defence of the United
Kingdom of Great Britain and Northern Ireland. The information may not
be used or disclosed otherwise that is provided for by the
above-mentioned licence without the prior written permission of the
Secretary of State, as represented by the Copyright Unit, Defence
Intellectual Property Rights, Poplar 2 \#2214, MOD Abbey Wood South,
Bristol BS34 8JH, UNITED KINGDOM.

CODA is provided on the basis that the US Government will disclose to
the UK Ministry of Defence (via AWE) any information, test results,
modifications or further developments based on or derived from the
disclosed information and will authorise the use of such information
for UK Government purposes on the same terms (i.e. under the terms of
the Creative Commons Attribution-NonCommercial- ShareAlike 4.0
International License (CC BY NC SA 4.0)).

For the avoidance of doubt, the Secretary of State of Defence for the
United Kingdom of Great Britain and Northern Ireland does not provide
any indemnity, and does not warrant the accuracy or completeness of
the information, nor does it warrant the suitability or completeness
of the information for any particular use or application.

Any requests for further use or disclosure of the information should,
in the first instance, be directed to AWE Commercial (via the Formal
Methods team at AWE).

\ifplastex
\subsubsection{Applicable Licences}
\label{sec:vhdl-applicable-licences}
\else
  \ifstandalone
  \subsubsection{Applicable Licences}
  \label{sec:vhdl-applicable-licences}
  \else
  \section{Applicable Licences}
  \label{sec:vhdl-applicable-licences}
  \fi
\fi
 
Unless otherwise indicated, all Content made available by the CODA
project is provided to you under the terms and conditions of one of
the following licences.

\begin{itemize}
\item The \emph{Creative Commons Attribution-NonCommercial-ShareAlike 4.0
    International License} (CC BY NC SA 4.0).  A copy of the \emph{CC BY NC SA
    4.0} is available at \url{https://creativecommons.org/licenses/by-nc-sa/4.0/legalcode}.

\item \emph{Eclipse Public License Version 1.0} (EPL) (available at 
   \url{http://www.eclipse.org/legal/epl-v10.html})
\end{itemize}

Content includes, but is not limited to, source code, object code,
documentation and other files maintained in the CODA repository (``Repository'').

The terms and conditions governing Features and Included Features
should be contained in files named ``licence.html'' (``Feature
Licences'').  Feature Licences may be located in any directory of a
Download or Module including, but not limited to the following
locations:

\begin{itemize}
\item Feature directories

\item Shared-licence feature \texttt{ac.soton.coda.licence}
\end{itemize}

Note: if a Feature made available by the CODA Project is
installed using the Eclipse Update Manager, you must agree to a
licence (``Feature Update Licence'') during the installation process.
If the Feature contains Included Features, the Feature Update
Licence should either provide you with the terms and conditions
governing the Included Features or inform you where you can locate
them.  Feature Update Licences may be found in the ``licence''
property of files named ``feature.properties'' found within a
Feature.  Such Feature Licences, and Feature Update
Licences contain the terms and conditions (or references to such
terms and conditions) that govern your use of the associated
Content in that directory.

THE FEATURE LICENCES, AND FEATURE UPDATE LICENCES MAY REFER
TO THE CC BY NC SA 4.0, EPL OR OTHER LICENCE AGREEMENTS, NOTICES OR TERMS AND
CONDITIONS.

IT IS YOUR OBLIGATION TO READ AND ACCEPT ALL SUCH TERMS AND
CONDITIONS PRIOR TO USE OF THE CONTENT.  If no Feature
Licence, or Feature Update Licence is provided, please contact the
CODA Project to determine what terms and conditions govern
that particular Content.
\begin{quote}
  \footnotesize

  \begin{itemize}
  \item  Java and all Java-based trademarks are trademarks of Sun
    Microsystems, Inc. in the United States, other countries, or
    both.
  \end{itemize}
\end{quote}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "user_manual"
%%% End:
