\appendix
\section{Release Notes}
\label{sec:release-notes}
\paragraph{1.0.0} The feature is now called CamilleX (instead of XEvent-B)
\begin{itemize}
\item Branding (0.0.4): Updated logo to CamilleX.
\item Common (0.0.5): Update copyright statements in source code.
\item Cheatsheets (1.0.0): Updated the name to use CamilleX instead of XEvent-B.
\item Documentation (1.0.0): Updated the name to use CamilleX instead of XEvent-B.
\item UI (0.1.0): Updated the name to use CamilleX instead of XEvent-B.
\item XContext (1.0.0): Updated the name to use CamilleX instead of XEvent-B.
  \begin{itemize}
  \item Update dependency ranges
  \end{itemize}
\item XContext IDE (1.0.0): Updated the name to use CamilleX instead of XEvent-B.
  \begin{itemize}
  \item Update dependency ranges
  \end{itemize}
\item XContext UI (1.0.0): Updated the name to use CamilleX instead of XEvent-B.
  \begin{itemize}
  \item Update dependency ranges
  \end{itemize}
\item XMachine (1.0.0): Updated the name to use CamilleX instead of XEvent-B.
  \begin{itemize}
  \item Update dependency ranges
  \end{itemize}
\item XMachine IDE (1.0.0): Updated the name to use CamilleX instead of XEvent-B.
  \begin{itemize}
  \item Update dependency ranges
  \end{itemize}
\item XMachine UI (1.0.0): Updated the name to use CamilleX instead of XEvent-B.
  \begin{itemize}
  \item Update dependency ranges
  \end{itemize}
\end{itemize}

\paragraph{0.0.7}
\begin{itemize}
\item XEvent-B Branding (0.0.3): Updated logo to XEvent-B.
\item XEvent-B Common (0.0.4): Enhancement (Issue \#11).
  \begin{itemize}
  \item Machines from different projects can now be included.

  \item  Machines are now included using qualified name defined as:
    \emph{projectName.machineName}
  \end{itemize}

\item  XEvent-B Documentations (0.0.7): Update documentation for 0.0.7 release.
\item  XEvent-B XContext (0.0.5): Changed dependency on XText to [2.12.0, 3.0.0).
\item  XEvent-B XContext IDE (0.0.4): Changed dependency on XText to [2.12.0, 3.0.0).
\item  XEvent-B XContext UI (0.0.4): Changed dependency on XText to [2.12.0, 3.0.0).
\item  XEvent-B XMachine (0.0.5):
  \begin{itemize}
  \item Changed dependency on XText to [2.12.0, 3.0.0).
  
  \item  Fixed Issue \#8: Comments are not parsed.
  
  \item  Fixed Issue \#10: Variants not translated: Fix is part of inclusion plug-in release 0.2.0.  
  
  \item  Flattened machines now have the included machine elements generated before the source machine.
  
  \item  Order of generating elements of multiple inclusions and/or instances is from last to first.
  
  \item  This update is part of inclusion plug-in release 0.2.0.
  \end{itemize}

\item  XEvent-B XMachine IDE (0.0.4): Changed dependency on XText to [2.12.0, 3.0.0).
\item  XEvent-B XMachine UI (0.0.4): 
  \begin{itemize}
  \item Changed dependency on XText to [2.12.0, 3.0.0).
  \item Regenerated from XEvent-B XMachine 0.0.5
  \end{itemize}
\end{itemize}

\paragraph{0.0.6}
\begin{itemize}
\item Renamed plug-ins and features to XEvent-B (instead of Event-B XText).
\item XEvent-B Branding (0.0.2): Renamed from Event-B XText Branding.
\item XEvent-B Documentations (0.0.2): Renamed from Event-B XText Documentations.
\item XEvent-B Cheatsheets (0.0.2): Renamed from Event-B XText Cheatsheets.
\item XEvent-B Common (0.0.3): Renamed from Event-B XText Common.
\item XEvent-B UI (0.0.2): Renamed from Event-B XText UI.
\item XEvent-B XContext (0.0.4): Renamed from Event-B XText Context.
\item XEvent-B XContext IDE (0.0.3): Renamed from Event-B XText Context IDE.
\item XEvent-B XContext UI (0.0.3): Renamed from Event-B Context UI.
\item XEvent-B XMachine (0.0.4): Renamed from Event-B XText Machine.
	\begin{itemize}
		\item Support Machine Inclusion and Event Synchronisation.
	\end{itemize}	
\item XEvent-B XMachine IDE (0.0.3): Renamed from Event-B XText Machine IDE.
\item XEvent-B XMachine UI (0.0.3): Renamed from Event-B XText Machine UI.
\end{itemize}

\paragraph{0.0.5}
\begin{itemize}
\item Event-B XText Documentations (0.0.1): Documentation plug-in (Initial version).
\end{itemize}

\paragraph{0.0.4}
\begin{itemize}
\item Updated plug-in dependency for the feature
\end{itemize}

\paragraph{0.0.3}
\begin{itemize}
\item Event-B XText Context (0.0.3):
  \begin{itemize}
  \item Issue \#3: Single-line comment after the element, multi-line comment before
    the element
  \end{itemize}

\item Event-B XText Context IDE (0.0.2): Regenerated
 
\item Event-B XText ContextUI IDE (0.0.2): Regenerated

\item Event-B XText Machine (0.0.3):
  \begin{itemize}
  \item Issue \#3: Single-line comment after the element, multi-line comment before
    the element.

  \item Issue \#5: Event terminator using 'end' keyword instead of ';'
  \end{itemize}

\item Event-B XText Machine IDE (0.0.2) Regenerated
  
\item Event-B XText Machine UI IDE (0.0.2) Regenerated
\end{itemize}


\paragraph{0.0.2}
\begin{itemize}
\item Event-B XText Common (0.0.2):
  \begin{itemize}
  \item Added transient value service for XContext and XMachine.
  \end{itemize}

\item Event-B XText Context (0.0.2):
  \begin{itemize}
  \item Added formatter (used for auto-indentation).
  \end{itemize}

\item Event-B XText Machine (0.0.2):
  \begin{itemize}
  \item Added formatter (used for auto-indentation).
  \end{itemize}

\item Event-B XText UI (0.0.1): Initial version
  \begin{itemize}
  \item Added context menu for converting machines and contexts to XText.
  \end{itemize}
\end{itemize}

\paragraph{0.0.1} Initial version contains the following plug-ins:
\begin{itemize}
\item Event-B XText Branding (0.0.1) Initial version: Branding information

\item Event-B XText Common (0.0.1) Initial version: Common facilities

\item Event-B XText Context (0.0.1) Initial version: Core support for Event-B contexts

\item Event-B XText Context IDE (0.0.1) Initial version: IDE for Event-B contexts

\item Event-B XText Context UI (0.0.1) Initial version: UI for Event-B contexts

\item Event-B XText Machine (0.0.1) Initial version: Core support for Event-B machines

\item Event-B XText Machine IDE (0.0.1) Initial version: IDE for Event-B machines

\item Event-B XText Machine UI (0.0.1) Initial version: UI for Event-B machines
\end{itemize}



%%% Local Variables:
%%% mode: latex
%%% TeX-master: "user_manual"
%%% End:
